### 2015-02-24 paper_30_measure.tex
completed Indicators, working on balanced scorecard

    \begin{itemize}
        \item Identify Process Issues
        \item Select And Define Measures
        \item Integrate with Software Process
    \end{itemize}

@@

    \subsection{METRICS}
        A \textit{metric} can be defined as a means of telling a complete story
        for the purpose of improving something \cite{Klubeck2011}.  Metrics are
        frequently indirect measurements. Metrics
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
            \item NOM - The Number of Methods per class
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics, as seen in the list above, for an SDO focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics alone is difficult.  That is why many of the other techniques
        build upon metrics to provide a more complete overall picture of an SDO.

    \subsection{INDICATORS}
        Another common measurement technique is indicators. An
        \textit{indicator} is simply a performance measure. 
        Typically, a number of indicators will be placed
        together and displayed in some report or on some
        dashboard. 
        Indicators can be crucial measurements
        within any business setting, and an SDO is no exception. Determining
        the correct indicators for an organization can
        be difficult, and many organizations incorrectly classify
        the indicators \cite{parmenter2010}.  
        The differences between the indicators will be explored and
        possible measures for each indicator in an SDO will be
        presented.   The four
        types of indicators important to an SDO are shown
        in Table \ref{tab:indicators}.

@@

                \caption{SOFTWARE DEFECT SEVERITY LEVELS}
                \label{tab:indicators}
            \end{longtable}

        \subsubsection{RESULT INDICATORS FOR SDO}
            More to come.

        \subsubsection{KEY RESULT INDICATORS FOR SDO}
            More to come.

        \subsubsection{PERFORMANCE INDICATORS FOR SDO}
            More to come.

        \subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}
            More to come.

        Antolic in \cite{Antolic2008} demonstrates some ways to measure KPIs for the  software development process.

@@

        A common technique for organizations to measure themselves is a balanced scorecard. \cite{kaplan1992}
        A \textit{balanced scorecard} must contain the following six
        characteristics.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Environment/Community
          \item Internal Process
          \item Employee Satisfaction
          \item Learning and Growth
        \end{enumerate}

@@

        This info comes from \cite{parmenter2010}.

>>>>

    \begin{enumerate}
        \item Identify Process Issues
        \item Select And Define Measures
        \item Integrate with Software Process
    \end{enumerate}

@@

    \subsection{METRICS}
        A \textit{metric} can be defined as a means of telling a complete story
        for the purpose of improving something \cite{Klubeck2011}.  Metrics are
        frequently indirect measurements and
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
            \item NOM - The Number of Methods per class
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics, as seen in the list above, for an SDO focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics alone is difficult.  That is why many of the other techniques
        build upon metrics to provide a more complete overall picture of an SDO. Metrics are great starting point, but more is needed to properly 
        evaluate performance.

    \subsection{INDICATORS}
    \label{sec:indicators}
        Another common measurement technique is indicators. An
        \textit{indicator} is simply a performance measure. 
        Typically, a number of indicators will be placed
        together and displayed in some report or on some
        dashboard. 
        Indicators can be crucial measurements
        within any business setting, and an SDO is no exception. Determining
        the correct indicators for an organization can
        be difficult, and many organizations incorrectly classify
        the indicators \cite{parmenter2010}.  
        The differences between the indicators will be explored and
        possible measures for each indicator in an SDO will be
        presented.   The four
        types of indicators important to an SDO are shown
        in Table \ref{tab:indicators}.

@@

            \caption{INDICATORS}
            \label{tab:indicators}
        \end{longtable}

        Indicators can be used in just about every organizational
        setting from businesses to non-profit organizations. They
        are not unique to SDOs, and the exact indicators to track
        is very specific to the organization.  The indicators chosen
        by one organization might not be the same as the indicators
        chosen by another organization.  The following sections
        will explain the type of indicators in more detail and provide
        some examples for an SDO.

        \subsubsection{RESULT INDICATORS (RI) FOR SDO}
            \textit{Result Indicators} are performance 
            measures that summarize activity.  All financial performance
            measures are result indicators.  Result indicators
            are measured on a timely basis (daily, weekly, monthly)
            and are the result of more than one activity.  They do not
            tell staff what needs to be done to improve the RI. For
            an SDO, some possible RIs are seen in Table \ref{tab:RI}.

            \begin{longtable}{@{}l l}
                \toprule%
                 \centering%
                 {\bfseries Result Indicators} &
                 \\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                % \midrule
                \endhead

                Requirements Implemented Per Month  \\
                \myrowcolour%
                Monthly SLOC \\
                New Weekly Users \\
                \myrowcolour%
                Monthly Development Hours \\
                Webpage Views Yesterday \\
                \myrowcolour%
                Monthly Development Hours \\
                Monthly Server Uptime \\
                \myrowcolour%
                Quartely Software Sales \\

                \caption{RESULT INDICATORS FOR AN SDO}
                \label{tab:RI}
            \end{longtable}

        \subsubsection{KEY RESULT INDICATOR (KRI) FOR SDO}
            \textit{Key Result Indicators} are measures of multiple
            activities that give a clear picture of whether the
            organization is traveling in the right direction.  Unfortunately,
            KRIs are commonly mistaken for KPIs \cite{parmenter2010}.  KRIs
            do not tell an organization what is needed to improve the 
            results.  KRIs are highly benefical for high-level management
            and not necessarily beneficial for staff working directly on 
            the software.  For
            an SDO, some possible KRIs are seen in Table \ref{tab:KRI}.

            \begin{longtable}{@{}l l}
                \toprule%
                 \centering%
                 {\bfseries Key Result Indicators} &
                 \\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                % \midrule
                \endhead

                Customer Satisfaction  \\
                \myrowcolour%
                Net Profit \\
                Money Spent on Fixing Software \\
                \myrowcolour%
                \% of New Features vs. Fixes \\
                Time on Website \\
                \myrowcolour%
                \% Servers Meeting the Expected Availability \\

                \caption{KEY RESULT INDICATORS FOR AN SDO}
                \label{tab:KRI}
            \end{longtable}

        \subsubsection{PERFORMANCE INDICATOR (PI) FOR SDO}
            \textit{Performance Indicators} are nonfinancial performance measures
            that help a team align themselves with the organizations 
            strategy.  These are important to the organizations success, but
            they are not the key measures that will lead to drastic improvement.  They are specifically tied to a team and all staff understand
            what actions need to be taken to improve the PI.
            For an SDO, some possible PIs are seen in Table \ref{tab:PI}.

            \begin{longtable}{@{}l l}
                \toprule%
                 \centering%
                 {\bfseries Performance Indicators} &
                 \\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                % \midrule
                \endhead

                \% Test Coverage\footnote{Test Coverage is simply the percentage 
                    of the code that is being tested. Ideally, this 
                    number would be 100\%, but higher is better.}   \\
                \myrowcolour%
                \# of Project Defects from Key Customers  \\
                Requirements Scheduled for Next Release  \\
                \myrowcolour%
                \# of Missed Requirements \\
                \% of Late Projects \\

                \caption{PERFORMANCE INDICATORS FOR AN SDO}
                \label{tab:PI}
            \end{longtable}

        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR SDO}
            \textit{Key Performance Indicators} are performance measures
            focusing on critical aspects for current and future organizational
            success.  Notice, KPIs are not focused on historical performance,
            and they clearly indicate how to drastically increase performance.
            KPIs allow a team to monitor current performance and 
            quickly take action to correct future performance.
            KPIs cover a shorter time frame than KRIs.
            KPIs consist of the following 7 characteristics \cite{parmenter2010}.
            \begin{enumerate}
                \item Not financial
                \item Measured frequently (hourly, daily, weekly)
                \item Acted on by CEO\footnote{Chief Executive Officer} 
                    and/or senior management
                \item Clearly indicate the action required
                \item Tie responsibility to a particular team
                \item Have a significant impact
                \item Encourage appropriate action
            \end{enumerate}

            Antolic in \cite{Antolic2008} made one of the earliest attempts
            to identify and measure the KPIs for an SDO. Antolic's strategy
            focused around 7 KPIs.
            \begin{enumerate}
                \item Schedule Adherence
                \item Assigned Content Adherence
                \item Cost Adherence
                \item Fault slip through
                \item Trouble report closure rate
                \item Cost per defect
            \end{enumerate}
            However, according to the definition of KPI just presented,
            they are not really KPIs but instead KRIs.  That is because
            none of the 7 clearly indicate the action required to 
            improve the measure.  Also, it is unclear if improving any of
            the measures will drastically improve performance.

            For an SDO, Table \ref{tab:KPI} identifies some more appropriate
            KPIs.

            \begin{longtable}{@{}l l}
                \toprule%
                 \centering%
                 {\bfseries Key Performance Indicators} &
                 \\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                % \midrule
                \endhead

                Projects more than 20\% behind schedule \\
                \myrowcolour%
                Servers currently unavailable \\
                Automated tests failing for more than 24 hours \\
                \myrowcolour%
                Projects with test coverage less than 60\% \\
                Projects with more than 10 SIT defects \\
                \myrowcolour%
                Unfixed, high priority PROD defects older than 1 week  \\

                \caption{KEY PERFORMANCE INDICATORS FOR AN SDO}
                \label{tab:KPI}
            \end{longtable}

@@

        A common technique for organizations to measure themselves is a 
        balanced scorecard, first presented by Kaplan and 
        Norton \cite{kaplan1992}.

        Kaplan and Norton originally identified 4 characteristics
        for the balanced scorecard, but 
        A \textit{balanced scorecard} should contain the following six
        characteristics with the final 2 being optional 
        as they were presented later by Parmenter \cite{parmenter2010}
        and are not considered as part of the original balanced
        scorecard outlined by Kaplan and Norton \cite{kaplan1992,Kaplan2007}.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction
          \item Environment/Community
        \end{enumerate}

@@

        This info comes from .
